MS Depression Paper, post replication, started 2022 09 21

### 2023-09-27 Biological_Psychiatry_Revision_Scripts/msdepression_n380_started_20230927_mm_BP_r1.Rmd
Add files via upload

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
library(ggplot2)
library(reshape2)
library(pwr)
library(mgcv)
library(boot)
library(boot.pval)
library(lsr)
library(sjPlot)
library(coin)
library(rstatix)
#library(effectsize)
library(colormod)
library(ggpubr)
library(ggsignif)

@@

@@

@@

@@

#clean up data frame
df_empi_dx_network_proportions <- dep_and_healthy_groups_for_ICD_analysis %>%
  mutate(subject = as.factor(EMPI)) %>%
  mutate(Diagnosis = ifelse(depGroupVar==1, "MS-Depression", "MS+Depression")) %>%
  mutate(Diagnosis = as.factor(Diagnosis)) %>%
  mutate(Dep_network = proportion_volume_lost_dep_net_by_network_size_sum) %>%
  mutate(Nondep_network = proportion_volume_lost_nondep_net_by_network_size_sum) %>%
  dplyr::select(subject, Diagnosis, Dep_network, Nondep_network, PAT_AGE_AT_EXAM) %>% 
  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  mutate(Network = as.factor(Network)) %>%
  ungroup()

@@

#with age; diagnosis: Dep > nondep T = 2.1, p = 0.035; Network dep>nondep = T=12.4, p = 2*10^-16; intx = T = 2.3, p = 0.020
diagnosis_by_network_interaction_lmer_age <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject) + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer_age)

@@

#Final data: 
#Main effect of network Dep > Nondep (Estimate = 0.09, 95% CI 0.076-0.104, P = 2*10^-16)
#Main effecet of diagnosis MS+Depression > MS-Depression (Estimate = 0.056, 95% CI 0.011-0.100, P= 0.015)
#Main effect of interaction (Estimate = 0.022, 95% CI 0.003 - 0.040, P=0.020)

@@

>>>>

#### New analyses per Biological Psychiatry Reviewer Recommendations from 9/26/2023

[x] Add sex into model - Reviewer 1

    - Main effect of network Dep > Nondep (Estimate = 0.090, 95% CI 0.076-0.10, P = 2*10^-16)
    - Main effects of diagnosis MS+Depression > MS-Depression (Estimate = 0.058, 95% CI  0.013-0.10, P= 0.012)
    - Main effect of sex M>F (Estimate = 0.021, 95% CI -0.061-0.020, P = 0.32)
    - Main effect of interaction (Estimate = 0.022, 95% CI 0.0035 - 0.040, P=0.020)

[x] Different thresholds for defining the depression network (using quartile breakdown for in/out) - Reviewer 1
  [x] Threshold the Harvard Mask at T>2.3 (P<0.01)

    - Main effect of network Dep > Nondep (Estimate = 0.048, 95% CI 0.037-0.058, P = 2*10^-16)
    - Main effects of diagnosis MS+Depression > MS-Depression (Estimate = 0.053, 95% CI 0.0085-0.098, P= 0.020)
    -Main effect of interaction (Estimate = 0.016, 95% CI 0.0028-0.030, P=0.019)

  [x] Threshold the Harvard Mask at T>2.6 (P<0.005)

    -Main effect of network Dep > Nondep (Estimate = 0.084, 95% CI 0.070-0.10, P = 2*10^-16)
    -Main effects of diagnosis MS+Depression > MS-Depression (Estimate = 0.056, 95% CI 0.011-0.10, P= 0.016)
    -Main effect of interaction (Estimate = 0.021, 95% CI 0.0032 - 0.039, P=0.021)

[x] Prevalence of depression in the PROMIS cohort - Reviewer 3

    - chi sq for prevalence? 49 promis scores in depressed group (out of 232); 36 promis scores in nondepressed group (out of 148)
    - X-squared = 0.21, p = 0.65, not significant

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
library(ggplot2)
library(reshape2)
library(pwr)
library(mgcv)
library(boot)
library(boot.pval)
library(lsr)
library(sjPlot)
library(coin)
library(rstatix)
#library(effectsize)
library(colormod)
library(ggpubr)
library(ggsignif)
#library(lspline)

@@

###new for BP
fascicle_volumes_dep_2_6 <- read.csv(paste0(homedir, "/results/streamline_volume_within_dep_network_2_6.csv"), header = T, sep = ",")

fascicle_volumes_dep_2_3 <- read.csv(paste0(homedir, "/results/streamline_volume_within_dep_network_2_3.csv"), header = T, sep = ",")

@@

#repeat for 2.3 and 2.6

@@

#testing whether PROMIS sub sample is equally representative with respect to prevalence of depression/non-depression. I.e. do more people with depression get PROMIS scores? or are we equally drawing from both groups?

#first number is # with depression, second is number without depression
num_w_promis <- c(sum(df_people_with_promis_data_scores_added_unique$depGroupVar == 2), sum(df_people_with_promis_data_scores_added_unique$depGroupVar == 1))

#first number is # with depression, second is number without depression
num_total <- c(sum(df_good_mimosa_unique_dep_and_healthy$depGroupVar == 2), sum(df_good_mimosa_unique_dep_and_healthy$depGroupVar == 1))

df_2x2_promis_score_by_total_people_per_diagnosis <- data.frame(cbind(num_w_promis, num_total), row.names = c("MS+Depression", "MS-Depression"))

#X-squared = 0.21, p = 0.65, not significant)
chisq <- chisq.test(df_2x2_promis_score_by_total_people_per_diagnosis)
```

@@

#clean up data frame
df_empi_dx_network_proportions <- dep_and_healthy_groups_for_ICD_analysis %>%
  mutate(subject = as.factor(EMPI)) %>%
  mutate(Diagnosis = ifelse(depGroupVar==1, "MS-Depression", "MS+Depression")) %>%
  mutate(Diagnosis = as.factor(Diagnosis)) %>%
  mutate(Dep_network = proportion_volume_lost_dep_net_by_network_size_sum) %>%
  mutate(Nondep_network = proportion_volume_lost_nondep_net_by_network_size_sum) %>%
  dplyr::select(subject, osex, Diagnosis, Dep_network, Nondep_network, PAT_AGE_AT_EXAM) %>% 
  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  mutate(Network = as.factor(Network)) %>%
  ungroup()

@@

#with age; diagnosis: Dep > nondep T = 2.1, p = 0.035; Network dep>nondep = T=12.4, p = 2*10^-16; intx = T = 2.3, p = 0.020; also tried with + lspline(PAT_AGE_AT_EXAM, knots = c(5)) instead of PAT_AGE_AT_EXAM, findings stayed the same so probs not modeling true spline
diagnosis_by_network_interaction_lmer_age <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject) + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer_age)

@@

#with sex; diagnosis: Dep > nondep T = 2.5, p = 0.012; sex: M>F = 1, p = 0.32; Network dep>nondep = T=12.4, p = 2*10^-16; intx = T = 2.3, p = 0.020
diagnosis_by_network_interaction_lmer_sex <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject) + osex, data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer_sex)

#Diagnosis: MS+ > MS- 0.013-0.10; sex: M>F 0.06 - -0.02 Network dep>nondep -.104--.076; intx: -0.040--0.003
confint(diagnosis_by_network_interaction_lmer_sex)

#Final data: 
#Main effect of network Dep > Nondep (Estimate = 0.09, 95% CI 0.076-0.104, P = 2*10^-16)
#Main effects of diagnosis MS+Depression > MS-Depression (Estimate = 0.056, 95% CI 0.011-0.100, P= 0.015)
#Main effect of interaction (Estimate = 0.022, 95% CI 0.003 - 0.040, P=0.020)

#final data with sex included:
#Main effect of network Dep > Nondep (Estimate = 0.090, 95% CI 0.076-0.10, P = 2*10^-16)
#Main effects of diagnosis MS+Depression > MS-Depression (Estimate = 0.058, 95% CI  0.013-0.10, P= 0.012)
#Main effect of sex M>F (Estimate = 0.021, 95% CI -0.061-0.020, P = 0.32)
#Main effect of interaction (Estimate = 0.022, 95% CI 0.0035 - 0.040, P=0.020)

@@

#### BP repeat analysis with depression threshold of 2.3 and 2.6

### Define Depression Network by Volume of Overlap for 2.3
```{r visualize_depression_network_volume}
###################################################
### Defining and Visualizing Depression Network ###
###################################################

######## Histograms for depression network
#first set the values to be the volumes
fascicle_volumes_dep_2_3_network_no_cranial_nerves <- fascicle_volumes_dep_2_3 %>% filter(fascicle %in% fascicle_names_no_cranial_nerves)

#set NAs to zero
fascicle_volumes_dep_2_3_network_no_cranial_nerves$non_zero_voxels_in_dep_map[is.na(fascicle_volumes_dep_2_3_network_no_cranial_nerves$non_zero_voxels_in_dep_map)] = 0

#sort based on overlap with depression depression map
fascicle_volumes_dep_2_3_network_no_cranial_nerves$fascicle <- factor(fascicle_volumes_dep_2_3_network_no_cranial_nerves$fascicle, levels = fascicle_volumes_dep_2_3_network_no_cranial_nerves$fascicle[order(fascicle_volumes_dep_2_3_network_no_cranial_nerves$non_zero_voxels_in_dep_map)])

#create data frame with fascicles sorted by overlap with depression network, replace abbreviations with full fascicle names and swap _ for space in the full name
df_fascicles_sorted_by_volume_in_mask <- fascicle_volumes_dep_2_3_network_no_cranial_nerves %>%  
  replace(is.na(.), 0) %>% 
  arrange(desc(non_zero_voxels_in_dep_map)) %>% 
  left_join(full_fascicle_names, by = c("fascicle" = "Abbreviation")) %>%
  mutate(full_fascicle_name_space = str_replace_all(Full_name, pattern = "_", replacement = " ")) %>%
  mutate(full_fascicle_name_space = str_replace(full_fascicle_name_space, pattern = " R$", replacement = " (Right)")) %>%
  mutate(full_fascicle_name_space = str_replace(full_fascicle_name_space, pattern = " L$", replacement = " (Left)")) %>%
  mutate(full_fascicle_name_space = gsub(pattern = "([0-9])", replacement = " \\1", x = full_fascicle_name_space))

write.table(df_fascicles_sorted_by_volume_in_mask, paste0(homedir, "/results/df_fascicles_sorted_by_volume_in_mask_2_3.csv"), quote = F, sep = ",") #had to manually change the spreadsheet because the dictionary is based on a spelling mistake - C_R_R is Cingulum Rarolfactory in the dictionary, but should be Parolfactory

#figure out how many fascicles are in top quartile
quartile <- round((dim(fascicle_volumes_dep_2_3_network_no_cranial_nerves)[1] / 4),0)

#sort all the fascicles by %overlap, in decreasing order (so highest overlap at the top), and then take names of the top quartile
dep_network_names_top_quartile_no_cranial_nerves_2_3<- (fascicle_volumes_dep_2_3_network_no_cranial_nerves[order(fascicle_volumes_dep_2_3_network_no_cranial_nerves$non_zero_voxels_in_dep_map, decreasing = TRUE),])$fascicle[1:quartile]

write.table(dep_network_names_top_quartile_no_cranial_nerves, paste0(homedir, "/results/dep_network_names_top_quartile_no_cranial_nerves_by_vol_2.3.txt"), row.names = F, col.names = F, quote = F)

df_for_making_binary_color_maps <- fascicle_volumes_dep_2_3_network_no_cranial_nerves %>% dplyr::select(fascicle, non_zero_voxels_in_dep_map)

write.table(df_for_making_binary_color_maps, paste0(homedir, "/results/volume_of_overlap_w_dep_net_n77_T_2_3.csv"), row.names = F, col.names = F, quote = F, sep = ",")

#get a network that includes all of the fascicles NOT in dep 25% network
dep_network_names_bottom_3_quartiles_no_cranial_nerves_2_3 <- fascicle_volumes_dep_2_3_network_no_cranial_nerves$fascicle[!(fascicle_volumes_dep_2_3_network_no_cranial_nerves$fascicle %in% dep_network_names_top_quartile_no_cranial_nerves_2_3)]

#top quartile, depression network
dep_network_total_volume_top_quartile_no_cranial_nerves_2_3 <-
sum(fascicle_volumes_dep_2_3_network_no_cranial_nerves$num_voxels_total[which(fascicle_volumes_dep_2_3_network_no_cranial_nerves$fascicle %in% dep_network_names_top_quartile_no_cranial_nerves_2_3)])

#bottom 3 quartiles, nondepression network
bottom_75_total_volume_no_cranial_nerves_2_3 <-
sum(fascicle_volumes_dep_2_3_network_no_cranial_nerves$num_voxels_total[which(fascicle_volumes_dep_2_3_network_no_cranial_nerves$fascicle %in% dep_network_names_bottom_3_quartiles_no_cranial_nerves_2_3)])

#### Calculate total volume in all non-cranial_nerve_network
total_volume_all_full_fascicles_2_3 <- dep_network_total_volume_top_quartile_no_cranial_nerves_2_3 + bottom_75_total_volume_no_cranial_nerves_2_3

plot_all_fascicle_volumes_dep_2_3_network_no_cranial_nerves <-ggplot(data = fascicle_volumes_dep_2_3_network_no_cranial_nerves, aes(x = fascicle, y=non_zero_voxels_in_dep_map))+
  ggtitle("Volume Overlap per Fascicle 2_3") + 
  geom_bar(stat="identity", fill="006300") +
  xlab("Fascicle") +
  ylab("Overlap with Depression Mask") +
  ylim(0,65000) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size=14),
        axis.title.x = element_text(size=14),
        axis.title.y = element_text(size=14),
        axis.line = element_line(size=1),
        panel.background = element_rect(colour = "white", fill = "white"))
print(plot_all_fascicle_volumes_dep_2_3_network_no_cranial_nerves)

#save pdf
pdf(file=paste0(homedir, "/results/Figures_for_msdepression_paper/plot_all_fascicle_volumes_dep_2_3_network_no_cranial_nerves.pdf"))
  plot_all_fascicle_volumes_dep_2_3_network_no_cranial_nerves
dev.off()

### Change names to add suffix
#replace each fascicle with vol suffix
dep_network_names_top_quartile_no_cranial_nerves_2_3 <- dep_network_names_top_quartile_no_cranial_nerves_2_3 %>% 
  gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #n=68, w/volume suffix

dep_network_names_bottom_3_quartiles_no_cranial_nerves_2_3 <- dep_network_names_bottom_3_quartiles_no_cranial_nerves_2_3 %>%
   gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #n=68, w/volume suffix

  #sum of total volume lost in depression network and proportion of volume lost in depression network (volume lost/network volume size) 
  mutate(sum_fascicle_vol_lost_indepnet_top_quartile_2_3 = 
           rowSums(across(all_of(dep_network_names_top_quartile_no_cranial_nerves_2_3)))) %>%
  mutate(proportion_volume_lost_dep_net_by_network_size_sum_2_3 = sum_fascicle_vol_lost_indepnet_top_quartile_2_3 /dep_network_total_volume_top_quartile_no_cranial_nerves_2_3) %>%

  #sum of total volume lost in nondepression network and proportion of volume lost in depression network (volume lost/network volume size) 
  mutate(sum_fascicle_vol_lost_nondep_bottom_3_quartiles_2_3 = 
           rowSums(across(all_of(dep_network_names_bottom_3_quartiles_no_cranial_nerves_2_3)))) %>%
  mutate(proportion_volume_lost_nondep_net_by_network_size_sum_2_3 = sum_fascicle_vol_lost_nondep_bottom_3_quartiles_2_3 /bottom_75_total_volume_no_cranial_nerves_2_3) %>%

#clean up data frame
df_empi_dx_network_proportions <- dep_and_healthy_groups_for_ICD_analysis %>%
  mutate(subject = as.factor(EMPI)) %>%
  mutate(Diagnosis = ifelse(depGroupVar==1, "MS-Depression", "MS+Depression")) %>%
  mutate(Diagnosis = as.factor(Diagnosis)) %>%
  mutate(Dep_network = proportion_volume_lost_dep_net_by_network_size_sum_2_3) %>%
  mutate(Nondep_network = proportion_volume_lost_nondep_net_by_network_size_sum_2_3) %>%
  dplyr::select(subject, osex, Diagnosis, Dep_network, Nondep_network, PAT_AGE_AT_EXAM) %>% 
  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  mutate(Network = as.factor(Network)) %>%
  ungroup()

#diagnosis: Dep > nondep T = 2.3, p = 0.02; Network dep>nondep = T=8.7, p = 2*10^-16; intx = T = 2.4, p = 0.019
diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer)

#Diagnosis: MS+ > MS- 0.009-0.10; Network dep>nondep -.04--.06; intx: -0.030--0.003
confint(diagnosis_by_network_interaction_lmer)

#with age; diagnosis: Dep > nondep T = 2.01, p = 0.046; Network dep>nondep = T=-8.7, p = 2*10^-16; intx = T = 2.4, p = 0.019
diagnosis_by_network_interaction_lmer_age <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject) + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer_age)

#Diagnosis: MS+ > MS- 0.001-0.9; Network dep>nondep -.04--.06; intx: -0.030--0.003; Age = 0.002=0.005
confint(diagnosis_by_network_interaction_lmer_age)

#with sex; diagnosis: Dep > nondep T = 2.4, p = 0.016; sex: M>F = 1, p = 0.32; Network dep>nondep = T=8.7, p = 2*10^-16; intx = T = 2.4, p = 0.020
diagnosis_by_network_interaction_lmer_sex <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject) + osex, data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer_sex)

#Diagnosis: MS+ > MS- 0.01-0.10; sex: M>F 0.06 - -0.02 Network dep>nondep -.04--.06; intx: -0.030--0.003
confint(diagnosis_by_network_interaction_lmer_sex)

#Final data: 
#Main effect of network Dep > Nondep (Estimate = 0.048, 95% CI 0.037-0.058, P = 2*10^-16)
#Main effects of diagnosis MS+Depression > MS-Depression (Estimate = 0.053, 95% CI 0.0085-0.098, P= 0.020)
#Main effect of interaction (Estimate = 0.016, 95% CI 0.0028-0.030, P=0.019)

#### BP repeat analysis with depression threshold of 2.6

### Define Depression Network by Volume of Overlap for 2.6
```{r visualize_depression_network_volume}
###################################################
### Defining and Visualizing Depression Network ###
###################################################

######## Histograms for depression network
#first set the values to be the volumes
fascicle_volumes_dep_2_6_network_no_cranial_nerves <- fascicle_volumes_dep_2_6 %>% filter(fascicle %in% fascicle_names_no_cranial_nerves)

#set NAs to zero
fascicle_volumes_dep_2_6_network_no_cranial_nerves$non_zero_voxels_in_dep_map[is.na(fascicle_volumes_dep_2_6_network_no_cranial_nerves$non_zero_voxels_in_dep_map)] = 0

#sort based on overlap with depression depression map
fascicle_volumes_dep_2_6_network_no_cranial_nerves$fascicle <- factor(fascicle_volumes_dep_2_6_network_no_cranial_nerves$fascicle, levels = fascicle_volumes_dep_2_6_network_no_cranial_nerves$fascicle[order(fascicle_volumes_dep_2_6_network_no_cranial_nerves$non_zero_voxels_in_dep_map)])

#create data frame with fascicles sorted by overlap with depression network, replace abbreviations with full fascicle names and swap _ for space in the full name
df_fascicles_sorted_by_volume_in_mask <- fascicle_volumes_dep_2_6_network_no_cranial_nerves %>%  
  replace(is.na(.), 0) %>% 
  arrange(desc(non_zero_voxels_in_dep_map)) %>% 
  left_join(full_fascicle_names, by = c("fascicle" = "Abbreviation")) %>%
  mutate(full_fascicle_name_space = str_replace_all(Full_name, pattern = "_", replacement = " ")) %>%
  mutate(full_fascicle_name_space = str_replace(full_fascicle_name_space, pattern = " R$", replacement = " (Right)")) %>%
  mutate(full_fascicle_name_space = str_replace(full_fascicle_name_space, pattern = " L$", replacement = " (Left)")) %>%
  mutate(full_fascicle_name_space = gsub(pattern = "([0-9])", replacement = " \\1", x = full_fascicle_name_space))

write.table(df_fascicles_sorted_by_volume_in_mask, paste0(homedir, "/results/df_fascicles_sorted_by_volume_in_mask_2_6.csv"), quote = F, sep = ",") #had to manually change the spreadsheet because the dictionary is based on a spelling mistake - C_R_R is Cingulum Rarolfactory in the dictionary, but should be Parolfactory

#figure out how many fascicles are in top quartile
quartile <- round((dim(fascicle_volumes_dep_2_6_network_no_cranial_nerves)[1] / 4),0)

#sort all the fascicles by %overlap, in decreasing order (so highest overlap at the top), and then take names of the top quartile
dep_network_names_top_quartile_no_cranial_nerves_2_6<- (fascicle_volumes_dep_2_6_network_no_cranial_nerves[order(fascicle_volumes_dep_2_6_network_no_cranial_nerves$non_zero_voxels_in_dep_map, decreasing = TRUE),])$fascicle[1:quartile]

write.table(dep_network_names_top_quartile_no_cranial_nerves, paste0(homedir, "/results/dep_network_names_top_quartile_no_cranial_nerves_by_vol_2.6.txt"), row.names = F, col.names = F, quote = F)

df_for_making_binary_color_maps <- fascicle_volumes_dep_2_6_network_no_cranial_nerves %>% dplyr::select(fascicle, non_zero_voxels_in_dep_map)

write.table(df_for_making_binary_color_maps, paste0(homedir, "/results/volume_of_overlap_w_dep_net_n77_T_2_6.csv"), row.names = F, col.names = F, quote = F, sep = ",")

#get a network that includes all of the fascicles NOT in dep 25% network
dep_network_names_bottom_3_quartiles_no_cranial_nerves_2_6 <- fascicle_volumes_dep_2_6_network_no_cranial_nerves$fascicle[!(fascicle_volumes_dep_2_6_network_no_cranial_nerves$fascicle %in% dep_network_names_top_quartile_no_cranial_nerves_2_6)]

#top quartile, depression network
dep_network_total_volume_top_quartile_no_cranial_nerves_2_6 <-
sum(fascicle_volumes_dep_2_6_network_no_cranial_nerves$num_voxels_total[which(fascicle_volumes_dep_2_6_network_no_cranial_nerves$fascicle %in% dep_network_names_top_quartile_no_cranial_nerves_2_6)])

#bottom 3 quartiles, nondepression network
bottom_75_total_volume_no_cranial_nerves_2_6 <-
sum(fascicle_volumes_dep_2_6_network_no_cranial_nerves$num_voxels_total[which(fascicle_volumes_dep_2_6_network_no_cranial_nerves$fascicle %in% dep_network_names_bottom_3_quartiles_no_cranial_nerves_2_6)])

#### Calculate total volume in all non-cranial_nerve_network
total_volume_all_full_fascicles_2_6 <- dep_network_total_volume_top_quartile_no_cranial_nerves_2_6 + bottom_75_total_volume_no_cranial_nerves_2_6

plot_all_fascicle_volumes_dep_2_6_network_no_cranial_nerves <-ggplot(data = fascicle_volumes_dep_2_6_network_no_cranial_nerves, aes(x = fascicle, y=non_zero_voxels_in_dep_map))+
  ggtitle("Volume Overlap per Fascicle 2_6") + 
  geom_bar(stat="identity", fill="006300") +
  xlab("Fascicle") +
  ylab("Overlap with Depression Mask") +
  ylim(0,65000) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size=14),
        axis.title.x = element_text(size=14),
        axis.title.y = element_text(size=14),
        axis.line = element_line(size=1),
        panel.background = element_rect(colour = "white", fill = "white"))
print(plot_all_fascicle_volumes_dep_2_6_network_no_cranial_nerves)

#save pdf
pdf(file=paste0(homedir, "/results/Figures_for_msdepression_paper/plot_all_fascicle_volumes_dep_2_6_network_no_cranial_nerves.pdf"))
  plot_all_fascicle_volumes_dep_2_6_network_no_cranial_nerves
dev.off()

### Change names to add suffix
#replace each fascicle with vol suffix
dep_network_names_top_quartile_no_cranial_nerves_2_6 <- dep_network_names_top_quartile_no_cranial_nerves_2_6 %>% 
  gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #n=68, w/volume suffix

dep_network_names_bottom_3_quartiles_no_cranial_nerves_2_6 <- dep_network_names_bottom_3_quartiles_no_cranial_nerves_2_6 %>%
   gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #n=68, w/volume suffix

  #sum of total volume lost in depression network and proportion of volume lost in depression network (volume lost/network volume size) 
  mutate(sum_fascicle_vol_lost_indepnet_top_quartile_2_6 = 
           rowSums(across(all_of(dep_network_names_top_quartile_no_cranial_nerves_2_6)))) %>%
  mutate(proportion_volume_lost_dep_net_by_network_size_sum_2_6 = sum_fascicle_vol_lost_indepnet_top_quartile_2_6 /dep_network_total_volume_top_quartile_no_cranial_nerves_2_6) %>%

  #sum of total volume lost in nondepression network and proportion of volume lost in depression network (volume lost/network volume size) 
  mutate(sum_fascicle_vol_lost_nondep_bottom_3_quartiles_2_6 = 
           rowSums(across(all_of(dep_network_names_bottom_3_quartiles_no_cranial_nerves_2_6)))) %>%
  mutate(proportion_volume_lost_nondep_net_by_network_size_sum_2_6 = sum_fascicle_vol_lost_nondep_bottom_3_quartiles_2_6 /bottom_75_total_volume_no_cranial_nerves_2_6) %>%

#clean up data frame
df_empi_dx_network_proportions <- dep_and_healthy_groups_for_ICD_analysis %>%
  mutate(subject = as.factor(EMPI)) %>%
  mutate(Diagnosis = ifelse(depGroupVar==1, "MS-Depression", "MS+Depression")) %>%
  mutate(Diagnosis = as.factor(Diagnosis)) %>%
  mutate(Dep_network = proportion_volume_lost_dep_net_by_network_size_sum_2_6) %>%
  mutate(Nondep_network = proportion_volume_lost_nondep_net_by_network_size_sum_2_6) %>%
  dplyr::select(subject, osex, Diagnosis, Dep_network, Nondep_network, PAT_AGE_AT_EXAM) %>% 
  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  mutate(Network = as.factor(Network)) %>%
  ungroup()

#diagnosis: Dep > nondep T = 2.4, p = 0.016; Network dep>nondep = T=11.9, p = 2*10^-16; intx = T = 2.3, p = 0.021
diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer)

#Diagnosis: MS+ > MS- 0.01-0.10; Network dep>nondep -0.07-0.10; intx: -0.003--0.04
confint(diagnosis_by_network_interaction_lmer)

#with age; diagnosis: Dep > nondep T = 2.01, p = 0.036; Network dep>nondep = T=-11.9, p = 2*10^-16; intx = T = 2.3, p = 0.021, age T = 4.3, P 2*1-^-5
diagnosis_by_network_interaction_lmer_age <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject) + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer_age)

#Diagnosis: MS+ > MS- 0.003-0.9; Network dep>nondep -.07--.10; intx: -0.04--0.003; Age = 0.002=0.006
confint(diagnosis_by_network_interaction_lmer_age)

#with sex; diagnosis: Dep > nondep T = 2.5, p = 0.013; sex: M>F = 1, p = 0.32; Network dep>nondep = T=11.9, p = 2*10^-16; intx = T = 2.3, p = 0.021
diagnosis_by_network_interaction_lmer_sex <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject) + osex, data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer_sex)

#Diagnosis: MS+ > MS- 0.01-0.10; sex: M>F 0.06 - -0.02 Network dep>nondep -.07--.09; intx: -0.04--0.003
confint(diagnosis_by_network_interaction_lmer_sex)

#Final data: 
#Main effect of network Dep > Nondep (Estimate = 0.084, 95% CI 0.070-0.10, P = 2*10^-16)
#Main effects of diagnosis MS+Depression > MS-Depression (Estimate = 0.056, 95% CI 0.011-0.10, P= 0.016)
#Main effect of interaction (Estimate = 0.021, 95% CI 0.0032 - 0.039, P=0.021)
